%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
      {Ultimate Frisbee}
      {}
      {} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
        \item {Ultimate (or ultimate Frisbee) is a low-contact team sport played with a flying disc, that is self-officated, even at the highest levels of competition.}
        \item {Been regularly playing this sport for the last 4-5 years after picking up the sport about 7-8 years ago.}
        \item {Been an integral part of the Leadership team of my club team for several years, apart from captaining the team for one season.}
        \item {Helped build and currently maintain an \href{https://rsvp.thatteidlikaalsoup.team/features}{RSVP/team management app} for our club team, that has been happily used by the team for 3+ years.}
        \item {Collaborated with a couple of others on my club team to produce a \href{https://www.instagram.com/tiks_ultimate/channel/}{series of interviews} with players on the team called the Humans of TIKS. I also built a \href{https://github.com/thatte-idli-kaal-soup/humans}{wrapper} around \texttt{ffmpeg} to edit the recordings, and to publish the videos.}
        \item {Selected to play on the Indian men's masters (players aged \ge 33 years) team in the \href{https://wmuc2020.com/}{World Masters Ultimate Championship 2020}. But, the tournament got cancelled due to COVID-19.}
        \end{cvitems}
      }
%---------------------------------------------------------
  \cventry
      {Ukulele}
      {}
      {} % Location
      {} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
        \item {I've been learning to play the Ukulele for the past 7-8 months, and it has been such a relief from all the pandemic/lockdown stress.}
        \item {Built an \href{https://ukulele.muse-amuse.in/}{aggregator site} for video tutorials for Indian songs. It is a \href{https://github.com/punchagan/ukulele-tutorials/}{React app} that lets learners search for tutorials based on Chords, Artists, Album, Language, etc. The video player also lets learners play a specific portion of the video in loop, to be able to practice by playing along.}
        \end{cvitems}
      }
%---------------------------------------------------------
\end{cventries}
