%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Mentoring}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
      {Mentor, Google Summer of Code (GSoC)}
      {Zulip \externallink{https://zulip.com}}
      {Remote} % Location
      {2018 --- 2020} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
        \item {GSoC is an international annual program in which Google awards stipends to students who successfully complete a free and open-source software coding project during the summer (\textasciitilde May to \textasciitilde Aug.).}
        \item {\textbf{2020}: Mentored a student who worked on migrating some legacy components from old tech stacks to newer ones. The student was an experienced contributor and didn't need too many inputs from me, apart from just talking about life in general and checking on them to make sure that the pandemic or other things weren't taking a toll on them.}
        \item {\textbf{2019}: Co-mentored two students, one of them who made improvements to the terminal client, and another student who worked on solidifying the email gateway and the message archive feature for Zulip. I helped the students by bouncing off ideas and reviewing some pull-requests.}
        \item {\textbf{2018}: Mentored a student who built a terminal client for Zulip using it's API. The terminal client was the student's idea, and he had a fair sense of what he wanted to work on. I helped debug some tricky race conditions, bounce off some ideas on how to implement some features, and reviewed some pull-requests.}
        \end{cvitems}
      }
%---------------------------------------------------------
  \cventry
      {Mentor}
      {Affinity Answers \externallink{https://www.affinityanswers.com}}
      {Bangalore, India} % Location
      {Jun. 2018 - Aug. 2018} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
        \item {Mentored a small team of 7-10 people to help improve their code quality and software development practices.}
        \item {Introduced ideas of pair programming, made a case for more tests and code reviews. Helped improve the git discipline in the team.}
        \item {Bounced off ideas for solving a bunch of different problems around collecting, analyzing and displaying data being collected.}
        \end{cvitems}
      }
%---------------------------------------------------------
\end{cventries}
